---
title: "Introduction"
subtitle: "Case Study 1"
---

```{r load_libraries, include=FALSE}
library(tidyverse)
```

## Background

Data intuition and insight is not rocket science. However, there is a science to data handling, visualization, and decision making with data. The material we cover this semester will introduce to topics around this science.

### Challenge

Make sure you understand the course objectives and that you are introduced to the material and tools of the course.

## Deliverables

* Complete the quizzes for the first two days of class in [Canvas](https://byui.instructure.com/)

## Class Meeting

### Objective 

During the first two days of the semester students will get oriented with the course and begin building a foundation of software and visualization skills to complete the objectives of this course.

### Topics Covered

* The structure and objectives of CSE 150 Data Intuition and Insight.
* The technology that will be used during the course.
* The reading material that will be used during the course.

## Readings

### Day 1  

* Watch [How Humans See Data](https://www.youtube.com/watch?v=fSgEeI2Xpdc)
* Read Good Charts (Type: Visualization)
  + Introduction
  + Chapter 1: A brief history of DataViz 

### Day 2 

* Read Good Charts (Type: Visualization)
  + Chapter 2: When a chart hits our eyes
* Read CSE 150: Data Intuition and Insight
  + Section 1.1: Tidy Data (Type: Data)
  + Sections 6.1.1 and 6.1.2: Google Sheets (Type: Tools)
  
## Class Notes  

### Day 1

[Learning Manifesto](https://datathink.io/my-learning-manifesto-aka-teaching-philosophy/)

Discussion based class

#### Outcomes

* Leave this class with marketable skills.
* Discover the joy of data literacy.
* Learn about the field of data science and data visualization.

#### Work in progress

We just finished the first draft of this class last Friday.

* We expect to have some hiccups along the way.
* Don’t panic! We are all learning together.
* Seth, Cannon, and Hathaway are all capable at visualization, but we will be learning Tableau with you.


[Implement what you learned](https://www.youtube.com/embed/kO8x8eoU3L4?rel=0&start=0)

Tab out your sheets

### Day 2

Above all else, show the data

#### Steps

1. We don't go in order
2. We see first what stands out
3. We see only a few things at once
4. We seek meaning and make connections
5. We rely on conventions and metaphors

#### Rephased

1. We don’t go in order
2. We see what stands out
3. Don’t fill up the plot
4. Humans yearn for patterns
5. Communication only happens through metaphor

#### Metaphor highlights

* South is down?
* Lighter color shades are “emptier” or lower than darker ones.
* Lines imply ordered relationship
* Time moves from left to right.
* After reading the chapter, what other metaphors could you use to describe visualization or elements of a visualization?

#### Good Chart Matrix

```{r pic, fig.align='center', out.width='75%'}
pic <- 'https://byuistats.github.io/CSE150/slides/images/gc/Intro_chartquadrant.png'
knitr::include_graphics(pic)
```

#### How data is stored.

Data and how to handle it isn’t trivial

* Visual consumption by humans
* Computer consumption for storage
* Analytics consumption

#### Tidy Structure

1. Each variable forms a column.
2. Each observation forms a row.
3. Each value must have its own cell.
  